---
title: "flat_first.Rmd for working package"
output: html_document
editor_options: 
  chunk_output_type: console
---

<!-- Run this 'development' chunk -->
<!-- Store every call to library() that you need to explore your functions -->

```{r development, include=FALSE}
library(testthat)
library(DBI)
library(RPostgres)
library(sf)
```

<!--
 You need to run the 'description' chunk in the '0-dev_history.Rmd' file before continuing your code there.

If it is the first time you use {fusen}, after 'description', you can directly run the last chunk of the present file with inflate() inside.
--> 

```{r development-load}
# Load already included functions if relevant
pkgload::load_all(export_all = FALSE)
```

# Include some data examples in your package

<!-- 
 Store your dataset in a directory named "inst/" at the root of your project.
 Use it for your tests in this Rmd thanks to `pkgload::load_all()` to make it available
and `system.file()` to read it in your examples.

- There already is a dataset in the "inst/" directory to be used in the examples below
-->

```{r development-dataset}
# Run all this chunk in the console directly
# There already is a dataset in the "inst/" directory
# Make the dataset file available to the current Rmd during development
pkgload::load_all(path = here::here(), export_all = FALSE)

# You will be able to read your example data file in each of your function examples and tests as follows - see chunks below
datafile <- system.file("shp_Vilaine.rdata", package = "geogwilenR")
load(file=datafile)

str(shp_Vilaine)
```


# Fonction pour charger une couche de geogwilen en mémoire

<!--
Create a chunk for the core of the function

- The chunk needs to be named `function` at least
- It contains the code of a documented function
- The chunk can also be named `function-my_median` to make it easily
findable in your Rmd
- Let the `@examples` part empty, and use the next `examples` chunk instead to present reproducible examples

After inflating the template

-  This function code will automatically be added in a new file in the "R/" directory
-->

```{r function}
#' charge_shp_geogwilen
#'
#' @param shp Name of the geogwilen table
#' @param scheme Name of the scheme were geogwilen table is stocked
#' @param shp_emprise sf object defining the extent of the query (optional)
#' @param col_geometry geometry name in the data 
#'
#' @return
#' sf object with result of the query
#' @export
#'
#' @examples
charge_shp_geogwilen <- function(shp, scheme, shp_emprise=NULL, col_geometry=NULL) {
  if (!is.null(shp_emprise)) {
    if (!inherits(shp_emprise, "sf")) {
    stop("shp_emprise should be a sf")
    }
  }
  
  if (!is.null(col_geometry)) {
    if (!inherits(col_geometry, "character")) {
    stop("col_geometry should be a character")
    }
  }
  
  # Se connecter à la base de données PostGIS
con <- dbConnect(RPostgres::Postgres(),
                 host = config$host,
                 port = config$port,
                 user = config$user,
                 password = config$password,
                 dbname = config$dbname)
   

# si la colonne geometry n'est pas explicitement nommée, on cherche l'existence d'une colonne geom ou geometry dans la base
if(is.null(col_geometry))
{# on recherche le nom de colonne geometry dans la base
col_names_query <- paste0("SELECT column_name FROM information_schema.columns 
                          WHERE table_schema = '",scheme,"' AND table_name = '",shp,"';")
col_names <- dbGetQuery(con, col_names_query)
col_names <- col_names$column_name

if(!("geom"%in%col_names | 
     "geometry"%in%col_names)){stop("impossible de determiner le nom de la colonne de geometry. Merci de renseigner le parametre col_geometry")}else{
       col_geometry<-ifelse("geom"%in%col_names,"geom", "geometry")
       }
  }

if (!is.null(shp_emprise)) {
  
  # Obtenir le SRID de la table
  srid_query <- paste0("SELECT Find_SRID('", scheme, "', '", shp, "', '", col_geometry, "') AS srid;")
  srid_result <- dbGetQuery(con, srid_query)
  srid <- srid_result$srid
  
  
  # reprojection en lambert 93 de shp_emprise
  shp_emprise<-st_transform(shp_emprise, st_crs=srid)
  
 
  # Convertir l'objet sf en WKT pour utiliser dans la requête SQL
emprise_wkt <- st_as_text(st_union(shp_emprise), EWKT = FALSE)


# Construire la requête SQL pour sélectionner les données
query <- paste0("SELECT * FROM \"",scheme,"\".\"",shp, "\" AS shp
                 WHERE ST_Within(",col_geometry,", ST_GeomFromText('", emprise_wkt, "', 2154));")

}else
{
  query <- paste0("SELECT * FROM \"",scheme,"\".\"",shp, "\";")
}
    
# Exécuter la requête et rapatrier les données
result <- st_read(con, query = query)

 # Fermer la connexion
  dbDisconnect(con)

return(result)
}
```

<!--
Create a chunk with an example of use for your function

- The chunk needs to be named `examples` at least
- It contains working examples of your function
- The chunk is better be named `examples-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This example will automatically be added in the '@examples' part of our function above in the "R/" directory
- This example will automatically be added in the vignette created from this Rmd template
-->

```{r examples}

config <- yaml::read_yaml("C://workspace//gwilenalim//yaml//config.yml")
# chargement de l'objet shp_Vilaine
datafile <- system.file("shp_Vilaine.rdata", package = "geogwilenR")
load(file=datafile)

# chargement du bv de la Vilaine
bv<-charge_shp_geogwilen(shp="bassin_vilaine", 
                     scheme="r300_territoire_sage")


# test de la fonction
pop_carroyee<-charge_shp_geogwilen(shp="filosofi2015_carreaux_200m_metropole", 
                     scheme="r350_eco_socio", 
                     shp_emprise=bv) 

pop_carroyee<-charge_shp_geogwilen(shp="Filosofi2017_carreaux_200m_bzh_pdl", 
                     scheme="r350_eco_socio", 
                     shp_emprise=bv) 

# test de la fonction
step<-charge_shp_geogwilen(shp="r621_step_vilaine_xy_ste", 
                     scheme="r621_step", 
                     shp_emprise=NULL) 


step_vilaine<-charge_shp_geogwilen(shp="bdd_step_fr", 
                     scheme="m621_step", 
                     shp_emprise=bv) 


# 
# options(viewer = NULL) 
# library(mapview)
# mapview(shp_Vilaine) + mapview(step_vilaine)
# 


```

<!--
Create a chunk with a test of use for your function

- The chunk needs to be named `tests` at least
- It contains working tests of your function
- The chunk is better be named `tests-my_median` to be handled
correctly when inflated as a vignette

After inflating the template

-  This test code will automatically be added in the "tests/testthat/" directory
-->

```{r tests}


config <- yaml::read_yaml("C://workspace//gwilenalim//yaml//config.yml")

# chargement du bv de la Vilaine
bv<-charge_shp_geogwilen(shp="bassin_vilaine", 
                     scheme="r300_territoire_sage")


# test de la fonction
pop_carroyee<-charge_shp_geogwilen(shp="filosofi2015_carreaux_200m_metropole", 
                     scheme="r350_eco_socio", 
                     shp_emprise=bv) 


test_that("charge_shp_geogwilen fonctionne sans emprise", {
  expect_true(inherits(bv, "sf"))
 expect_true(nrow(bv)>=1)
})

test_that("charge_shp_geogwilen fonctionne avec emprise", {
  expect_true(inherits(pop_carroyee, "sf"))
 expect_true(nrow(pop_carroyee)>1)
})

```


<!--
# There can be development actions

Create a chunk with 'development' actions

- The chunk needs to be named `development` or `dev`
- It contains functions that are used for package development only
- Note that you may want to store most of these functions in the 0-dev_history.Rmd file

These are only included in the present flat template file, their content will not be part of the package anywhere else.
-->

```{r development-inflate, eval=FALSE}
# Keep eval=FALSE to avoid infinite loop in case you hit the knit button
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_first.Rmd", vignette_name = "Get started")
```


# Inflate your package

You're one inflate from paper to box.
Build your package from this very Rmd using `fusen::inflate()`

- Verify your `"DESCRIPTION"` file has been updated
- Verify your function is in `"R/"` directory
- Verify your test is in `"tests/testthat/"` directory
- Verify this Rmd appears in `"vignettes/"` directory
